---
title: "VariantBench -- benchmarking variant access and analysis"
author: "Vincent J. Carey, stvjc at channing.harvard.edu"
date: "`r format(Sys.time(), '%B %d, %Y')`"
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{VariantBench -- benchmarking variant access and analysis}
  %\VignetteEncoding{UTF-8}
output:
  BiocStyle::pdf_document:
    toc: yes
    number_sections: yes
  BiocStyle::html_document:
    highlight: pygments
    number_sections: yes
    theme: united
    toc: yes
---

# Introduction

We will illustrate a simple use of the harness for
multiple approaches to VCF access.  We have a local
version of the Tabix-indexed VCF for chr17 for 1000 genomes.
We'll set up packages and path.
```{r setup}
suppressPackageStartupMessages({
library(VariantBench)
library(GenomicRanges)
})
loc17 = "/Users/stvjc/Research/VCF/ALL.chr17.phase3_shapeit2_mvncall_integrated_v5.20130502.genotypes.vcf.gz"
```

An illustrative _closure_ is provided that encapsulates
the information about the VCF to be processed.
```{r lkclo}
useScanVcfClo
```

We bind the file path to the VCF processing function.
```{r lkclo2}
useScanVcf_local = useScanVcfClo(loc17)
useScanVcf_local 
ls(environment(useScanVcf_local))
```

Now run the harnessed processing function.
```{r dorun}
vbHarness(GRanges("17", IRanges(16e6, 16.01e6)), 
    list(useScanVcf=useScanVcf_local))
```

We can collect information on multiple request types
by iterating over ranges of various widths.
```{r setiter}
rngs = GRanges("17", IRanges(16e6, width=c(1e4, 2e4, 5e4, 1e5)))
multperf = lapply(rngs, function(r)
  vbHarness(r, list(useScanVcf=useScanVcf_local)))
```

The following overcomplicated functions extract key information
about performance.  These are fragile to details of the
output of the method passed to the harness.
```{r deff}
widths = function(x) sapply(x, sapply, 
  function(y) width(y$request))
meantimes = function(y)apply(sapply(y, 
    function(x) (x$useScanVcf$timing$time)), 2, mean)
```

This permits a plot like
```{r dopl, fig=TRUE}
plot( widths(multperf), meantimes(multperf)/10^6, type="b",
  xlab="request width in bp", ylab="time in microsec")
```

